%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Shreyas Narasimhiah Ramesh} \\ \vspace{1pt}
    San Diego, California 92115 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 619-918-5304 ~ \href{mailto:snarasimhiahra1451@sdsu.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{snarasimhiahra1451@sdsu.edu}} ~ 
    \href{https:www.linkedin.com/in/shreyas-n-r}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/shreyas-n-r}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Shreyas-NR}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Diego State University}{Expected Graduation - May 2023}
      {Master of Science in Electrical Engineering.}{San Diego, CA, USA}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Aug. 2014 -- Jul. 2017}
      {Bachelor of Engineering in Electronics and Communication Engineering.}{Bengaluru, KA, INDIA}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Embedded Systems
%                 \item Machine Learning
%                 \item Embedded OS
%                 \item Control Systems
%                 \item Digital Electronics
%                 \item Analog Electronics
%                 \item Stochastic Signals \& Systems
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CPDM, Indian Institute of Science}{Jul. 2020 -- Aug. 2021}
      {Project Associate - Embedded Systems Engineer.}{Bengaluru, India.}
      \resumeItemListStart
        \resumeItem{Developed and architected firmware for closed-loop control of a system that extends preservation time of the heart through active cooling and intermittent perfusion on an STM32(Cortex M4) based microcontroller.}
        \resumeItem{Designed and developed a GUI for accepting User inputs and monitoring active temperature, pH, inline pressure, and strain gauge sensors using the Qt framework and Python (pyqt5) on RaspberryPi 4 hardware.}
        \resumeItem{Designed and brought up a customized PCB to interconnect all the submodules of the complete system to a central control board.}
        \resumeItem{Procured necessary components with appropriate certifications suitable for medical devices.}
      \resumeItemListEnd

    \resumeSubheading
      {Panacea Medical Technologies Pvt. Ltd.}{Jan 2018 -- Oct 2019}
      {Design Engineer - Embedded Systems Engineer.}{Bengaluru, India.}
      \resumeItemListStart
        \resumeItem{RTL / Logic development in Verilog for Xilinx Spartan 6 FPGA.}
        \resumeItem{Low-Level Peripheral driver development on SPI, I2C, CAN, GPIO, Timer, PWM, and UART for LPC1788 microcontroller.}
        \resumeItem{Board schematic design using Orcad, and Board bring up with necessary test plan.}
        \resumeItem{Hardware Level Debugging using tools such as Multimeter, Oscilloscope, and Logic analyzer.}
        \resumeItem{Participation with interdisciplinary teams to design a module of the product.}
        \resumeItem{Experience in building backend Windows Application using C\# on Visual Studio IDE.}
        \resumeItem{Version control using Git with Microsoft Team Foundation Server.}
    \resumeItemListEnd
    
    \resumeSubheading
      {SOCDV Technologies Pvt. Ltd.}{Jul. 2017 -- Dec. 2017}
      {Physical Design Engineer Intern.}{Bengaluru, India.}
      \resumeItemListStart
        \resumeItem{Die area and Core area creation, Design of Different Floorplan, Multi-Voltage Design using different Scenarios MCMM(multi-corner multi-mode).}
        \resumeItem{Placement of Standard cell and Legalizing cells, Generation of Timing Reports, Analyse Setup and Hold Slack for MET or Violated.}
        \resumeItem{ECO on individual StdCell and its Nets, Buffer, and inverter cell insertion.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{Robot simulation using ROS } $|$ \emph{ROS, Gazebo, RVIZ, Ubuntu 18.04}}{Apr. 2020 -- May 2020}
          \resumeItemListStart
            \resumeItem{Visualization and creation of a custom environment with a robot with necessary ROS communication tools.}
            \resumeItem{Mapped the robot environment and navigation with a mobile robot.}
            \resumeItem{Implemented a pick-and-place function with industrial robot arms and state machines for the overall application.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{360' Surveillance Self-Balanced Rover} $|$ \emph{Embedded C++, Arduino, Gyroscope, nRF24L01}}{Jan. 2017 -- Jul. 2017}
          \resumeItemListStart
            \resumeItem{Built a prototype of a two-wheeled robot that can balance using the principle of the gyroscope.}
            \resumeItem{Implemented a closed-loop control system to maintain the orientation of the rover using a PID controller.}
            \resumeItem{Developed a joystick-based wireless remote to control the rover using nRF24l01 transceivers modules.}
          \resumeItemListEnd
          \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{Advanced Railway Management System} $|$ \emph{LPC2148, Keil µVision, GSM-GPS, Relay}}{Jan. 2014 -- May 2014}
          \resumeItemListStart
            \resumeItem{Built a prototype of a railway system consisting of a metro train model with a track and a station integrated with all the electronics for the automation of the system.}
            \resumeItem{Developed an automated system firmware for both the railway staff and the passenger's comfort and safety on LPC 2148, microcontroller interfacing DC motor, GPS \& GSM module, Temperature \& smoke sensor, RFID modules, and 32x4 LCD.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Embedded-C, Verilog, C Programming, Python, C\#, and basics of TCL.} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Keil µVision, STM32Cube, PyCharm, MATLAB, Xilinx ISE.} \\
     \textbf{Programming Platforms}{: ARM cortex M3\&M4, NXP LPC1768/1788, STM32F4/L4, LPC2148, 89C51.} \\
     \textbf{Hardware Design}{: Schematic design and BOM generation using Orcad Capture, PCB layout using Eagle, Machine Wiring diagram.} \\
     \textbf{Technologies/Frameworks}{: Linux, GitHub, PyQt.} \\
    }}
 \end{itemize}
 \vspace{-16pt}


% %-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%             \resumeItemListStart
%                 \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                 \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                 \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}
